### 2017-02-08 doc/manuscript.Rmd
Added interaction with time, sex, ethnicity unadjusted results in Results

```{r load_data, message=FALSE, echo=FALSE}
devtools::load_all('.')
ds0yr <- project_data %>% 
    dplyr::filter(VN == 0)
```

@@

Both clinically-measured TAG and total TAGFA concentration had very strong
negative associations with all outcome variables. There were no significant
interactions by time, sex, or ethnicity for any of the TAGFA (data not shown).
We ran sensitivity analyses to identify which covariate attenuated the beta-cell
function associations from the unadjusted model. We found that including waist
circumference in the model lead to the attenuation of associations, shown in 
`r cite_st("gee_adj_nowaist")`. A tabular presentation of the GEE results is
shown in `r cite_st("gee_unadj")` for unadjusted models and 
`r cite_st("gee_adj")` for adjusted models.

>>>>

```{r load_data, message=FALSE, echo=FALSE}
devtools::load_all('.')
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    dplyr::filter(VN == 0)
```

@@

Both clinically-measured TAG and total TAGFA concentration had very strong
negative associations with all outcome variables. While there were a few
significant interactions by time in unadjusted models, after inclusion of
covariates in the model, these interactions were attenuated (data not
shown). There were no significant interactions by sex or ethnicity for any of
the TAGFA (data not shown). We ran sensitivity analyses to identify which
covariate attenuated the beta-cell function associations from the unadjusted
model. We found that including waist circumference in the model lead to the
attenuation of associations, shown in `r cite_st("gee_adj_nowaist")`. A tabular
presentation of the GEE results is shown in `r cite_st("gee_unadj")` for
unadjusted models and `r cite_st("gee_adj")` for adjusted models.
